The symmetry of partner modelling

### 2016-02-04 mutual-modeling.tex
Split section 4 and created a new section 'Hypotheses and questions'

\subsubsection*{Hypotheses}

The experiments we report here address mutual modelling across different tasks,
some with dyads, other with triads. They were conducted along 6 years in two
different institutions by different researchers. They used different
independent, intermediate and dependent variables. Nonetheless, we were able to
address a few questions across these studies. We start with 3 simple hypotheses
about $\mathcal{M}^{\circ}(A,B)$:

@@

One interesting question relates to the symmetry of mutual modelling: what is
the relationship between \Model{A}{B}{X} and \Model{B}{A}{X}
(Fig.~\ref{mm_symmetry})? A low symmetry would mean that mutual modelling is
mainly an individual attitude/aptitude ($\mathcal{H}_{1}$). A high correlation
might support $\mathcal{H}_{2}$ or $\mathcal{H}_{3}$ since there is a low
probability that randomly formed pairs integrate peers with the same level of
mutual modelling skills.

@@

With triads, we may compute the accuracy of 6 models:
\Model{A}{B}{X}, \Model{B}{A}{X}, \Model{A}{C}{X}, \Model{C}{A}{X},
\Model{C}{B}{X} and \Model{B}{C}{X}.

This leads to two \emph{triangle questions} (Fig.~\ref{mm_triangles}): Do $A$
and $B$ have the same accuracy when modelling $C$ ($\Delta_2 =
\Delta(\mathcal{M}^{\circ}(A,C,X), \mathcal{M}^{\circ}(B,C,X))$)? If it is the
same, $\mathcal{H}_{2}$ and $\mathcal{H}_{3}$ gains over $\mathcal{H}_{1}$

Conversely, does $C$ model more accurately $A$ than $B$ ($\Delta_3=
\Delta(\mathcal{M}^{\circ}(C,A,X), \mathcal{M}^{\circ}(C,B,X))$)? A positive
answer would support $\mathcal{H}_{3}$. A negative answer would support
$\mathcal{H}_{2}$ since $\Delta_3$ could mainly be explained by the way $A$ and
$B$ help $C$ to model them.

@@

In addition, the comparison between $\Delta_2$ and $\Delta_3$ could tell us
whether the accuracy of mutual modelling depends more upon the modeller's effort
or the modellee's behaviour.

@@

We can go further by comparing self- versus other modelling ($\Delta_4$ in
Fig.~\ref{mm_rectangle}) as an indication of meta-cognitive skills. We can also
question if modelling skills depend upon what aspects are being modeled ($X$ or
$Y$), which would explain vertical differences ($\Delta_5$ in
Fig.~\ref{mm_rectangle}). When possible, we will also discuss these two
questions in the studies presented hereafter.

@@

\caption{\small Meta-cognitive skills and domain-dependent modelling}

@@

This simple notation does not pretend to provide a mathematical account of
mutual modelling but to be more systematic in describing the following
experiments.

>>>>

\section*{Hypotheses and questions}

The experiments we report here address mutual modelling across different tasks,
some with dyads, other with triads. They were conducted along 6 years in two
different institutions by different researchers. They used different
independent, intermediate and dependent variables. Nonetheless, we were able to retroactively
address 3 research questions across these studies.

As stated earlier, the fundamental challenge is to determine if mutual modelling is an individual skill (hypothesis 1) or  the emergent property of social interactions (hypothesis 3).  This question is empirically translated into the symmetry of mutual modelling: what is
the relationship between \Model{A}{B}{X} and \Model{B}{A}{X}
(Fig.~\ref{mm_symmetry})? A low symmetry would mean that mutual modelling is
mainly an individual attitude/aptitude ($\mathcal{H}_{1}$). A high correlation
might support $\mathcal{H}_{3}$ since there is a low
probability that randomly formed pairs integrate peers with the same level of
mutual modelling skills. However, a high correlation could also have another explanation, stated in  $\mathcal{H}_{2}$: it could be that A is good at modelling B and good at helping B to model herself or himself.

@@

@@

With triads, we may compute the accuracy of 6 models:
\Model{A}{B}{X}, \Model{B}{A}{X}, \Model{A}{C}{X}, \Model{C}{A}{X},
\Model{C}{B}{X} and \Model{B}{C}{X}.This leads to two \emph{triangle questions} (Fig.~\ref{mm_triangles}): Do $A$
and $B$ have the same accuracy when modelling $C$ ($\Delta_2 =
\Delta(\mathcal{M}^{\circ}(A,C,X), \mathcal{M}^{\circ}(B,C,X))$)? A significant correlation would support
, $\mathcal{H}_{2}$  (C has helped both A and B to model C) or support $\mathcal{H}_{3}$ (the quality of triad interactions enables all partners to model each other accurately)

Conversely, does $C$ model more accurately $A$ than $B$ ($\Delta_3=
\Delta(\mathcal{M}^{\circ}(C,A,X), \mathcal{M}^{\circ}(C,B,X))$)? A positive
answer would support $\mathcal{H}_{1}$, C being simply good at modelling any partner.  It could also support  $\mathcal{H}_{3}$,  since the quality of interactions influences the accuracy of two models that C is building. A negative answer would support
$\mathcal{H}_{2}$ since $\Delta_3$ could mainly be explained by the fact that  $A$ helped more $C$ to model him than 
$B$ did.

In addition, the comparison between $\Delta_2$ and $\Delta_3$ could tell us
whether the accuracy of mutual modelling depends more upon the modeller's effort  $\mathcal{H}_{1}$
or the modellee's behaviour  $\mathcal{H}_{2}$.

Please note that we consider the quality of interactions at triad level (ABC), neglecting the cases where AB interact better for instance than BC, since there was no 'private' communication channel in the following studies. We do nonetheless acknowledge that this point could be debated.

@@

@@

We can go further by comparing self- versus other modelling ($\Delta_4$ in
Fig.~\ref{mm_rectangle}). A large difference would indicate that meta-cognitive skills (self-modelling) and partner modelling skills are rather different skills, while a small $\Delta_4$ could be interpreted as the indications that these are two specific instance of a more general cognitive process. This questions is however not central to this paper, and the value of $\Delta_4$ us only available in one of the reported studies.

 We can also question if modelling skills depend upon what aspects are being modeled ($X$ or
$Y$), which would explain vertical differences ($\Delta_5$ in
Fig.~\ref{mm_rectangle}).  These differences would allow refining the notion of modelling skills, namely whether there exist some general ability to model partners or whether this is only the abstraction of a beam of more specific skills such as detecting emotions versus identifying references from deictic gestures.

@@

\caption{\small Meta-cognitive skills (horizontally) and domain-dependent modelling (vertically}

@@
